---
title: "Lab2.rmd"
author: "Kevin Zhai"
date: "10/31/2016"
output: pdf_document
---
1.
```{r}
wine <- read.csv(file="redwine.txt",head=TRUE,sep="\t")
mean(wine$RS, na.rm = T)
mean(wine$SD, na.rm = T)
```
The average of RS is 2.53 and the average of SD is 46.2 when we ignore the NA values.

2. 
```{r}
SDFS <- cbind(wine$SD,wine$FS)
SDFS.omit <- na.omit(SDFS)
reg <- lm(SDFS.omit[,1] ~ SDFS.omit[,2])
coef(reg)

```
The coefficients for the Intercept and FS are 13.18 and 2.08 respectively. 

3. 
```{r}
#Function for imputing using SDFS Regression Model 
reg.imp <- function (a){
       missing <- is.na(a)                
       n.missing <- sum(missing)     
       a.obs <- a[!missing]
       imputed <- a
       imputed[missing] <- 2.08*SDFS[is.na(SDFS[,1])][18:34] + 13.18
       return (imputed)
}
wine$SD <- reg.imp(wine$SD)
mean(wine$SD)

```
The average value of SD is now 46.3.

4.
```{r}
avg.imp <- function (a, avg){
        missing <- is.na(a)
        n.missing <- sum(missing)
        a.obs <- a[!missing]
        imputed <- a
        imputed[missing] <- avg
       return (imputed)
}
wine$RS <- avg.imp(wine$RS,mean(wine$RS, na.rm = T))
mean(wine$RS)

```
The average stays the same at 2.53, which is the intuitive answer. 

5.
```{r}
winemodel <- lm(wine$QA~wine$FA+wine$VA+wine$CA+wine$RS+wine$CH+wine$FS+wine$SD+wine$DE+wine$PH+wine$SU+wine$AL)
coef(winemodel)

```
6.
```{r}
summary(winemodel)
```
Based on the predictor with the highest p-value, PH seems to be the the one that is least likely related to QA. The p-value is 0.41, which is very unsignificant. 

7. 
```{r}
library(DAAG)
validation <- CVlm(data = wine, QA~FA+VA+CA+RS+CH+FS+SD+DE+PH+SU+AL, m=5)
```
The average error rate is 0.426.

8.
```{r}
phmean <- mean(wine$PH)
phsd <- sd(wine$PH)
cutoff <- c(phmean - 3*phsd,phmean +3*phsd)
redwine2 <- subset(wine, wine$PH<4.48 & wine$PH>2.13)
str(redwine2)
```
19 observations are removed.

9.
```{r}
winemodel2 <- lm(redwine2$QA~redwine2$FA+redwine2$VA+redwine2$CA+redwine2$RS+redwine2$CH+redwine2$FS+redwine2$SD+redwine2$DE+redwine2$PH+redwine2$SU+redwine2$AL)
summary(winemodel2)
```
This model is slightly better, with a higher R^2 value and adjusted R^2. Based on the p-values, the 5 best predictors are VA, CH, SD, SU, and AL.  
